Equalizer 2.0\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Results for data compression engines
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@26 db7c848b-7755-4df2-b763-8796797afa52

RSP is optimized for LAN performance. In the following we will outline the RSP
protocol and implementation and motivate the design decisions. Any defaults
given below are for Linux or OS X, the Windows UDP stack requires different
default values which can be found in the implementation.

@@

The \textsf{\_appBuffers} queue, which is blocking, contains received UDP
datagrams on incoming connections, or empty buffers for writing on outgoing
connections. The \textsf{\_threadBuffers} queue is lock-free and used by the
protocol thread to store empty buffers on incoming connections and pre-packaged
UDP datagrams on outgoing connections. The application thread pushes buffers
into this queue, consumed by the protocol thread. A datagram is up to 64
kilobytes (UDP limit, configurable) and contains a header (two bytes type, two
bytes size, two bytes source identifier, two bytes sequence number) and its
payload. The sequence number is used for positive (ack) and negative (nack)
acknowledgments and reordering of packets.

@@

>>>>

RSP combines various established algorithms~\cite{nack, flowcontrol} for
multicast in an open source implementation capable of delivering wire speed
transmission rates on high-speed LAN interfaces. In the following we will
outline the RSP protocol and implementation and motivate the design
decisions. Any defaults given below are for Linux or OS X, the Windows UDP stack
requires different default values which can be found in the implementation.

@@

The \textsf{\_appBuffers} queue, which is blocking, contains received UDP
datagrams on incoming connections, or empty buffers for writing on outgoing
connections. The \textsf{\_threadBuffers} queue is lock-free and used by the
protocol thread to store empty buffers on incoming connections, and pre-packaged
UDP datagrams on outgoing connections. The application thread pushes buffers
into this queue, consumed by the protocol thread. A datagram is up to 64
kilobytes (UDP limit, configurable) and contains a header (two bytes type, two
bytes size, two bytes source identifier, two bytes sequence number) and its
payload. The sequence number is used for positive (ack) and negative (nack)
acknowledgments and reordering of packets.

@@

\begin{figure}[ht]\center
  \includegraphics[width=\columnwidth]{images/compressor}
  \caption{\label{fCompressor}Data Compression Engines}
\end{figure}
